Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2013-10-26 paper/ms.tex
Discusion on the Walker-Soler paper in the introduction section

@@

In this \documentname we implement a method to populate the DM halos
in cosmological simulations with LAEs that bypasses all the
uncertainty involved in the estimation of star formation rates and \ly escape
fraction. The model only considers whether a DM can host a
detectable LAE or not without predicting a \ly  luminosity. Once the
mock catalogs are constructed  we proceed with a direct comparison
against the statistics derived from observations. This allows us 
to find the preferred mass range of DM halos hosting these galaxies
and its occupation fraction.

>>>>

{\bf \cite{Soler2012} has derived the median mass of $z=0$ the $z=3.1$ LAE 
descendat.  In order to construct their  LAE mock catalogs 
they impose their model to reproduced, whitin the observational errors,
 the number density  as well as  the minimal and median mass reported 
 by \cite{Gawiser07} that has been derived from observations
 over one single field. }

@@

In this \documentname we implement a method to populate the DM halos
in cosmological simulations with LAEs that bypasses all the
uncertainty involved in the estimation of star formation rates and \ly escape
fraction. The model only considers whether a DM can host a
detectable LAE or not without predicting a \ly  luminosity. Once the
mock catalogs are constructed  we proceed with a direct comparison
against the statistics on the number density distribution derived from
 the observations over the 12 fields of \cite{Yamada2012}. This allows us 
to find the preferred mass range of DM halos hosting these galaxies
and its occupation fraction.
